\documentclass[]{report}


\usepackage{amsmath} %General package for maths (loads also amsbsy to make bold symbols)
\usepackage{amsthm} %Package for theorems
\usepackage{amssymb} %Symbols (loads also amsfonts)


% Title Page
\title{}
\author{}


\begin{document}
	
	\begin{center}
		\textbf{	Comments Revision JFA-19-244}
	\end{center}
During the last revision, we realized that we were not precise enough regarding some estimates appearing in Remark~3.4. Indeed, estimates (3.8) and (3.9) require some regularity on the kernel of the operator $L_K$. Although this regularity is fulfilled by the operators that we consider in this paper (that is, satisfying the convexity assumption (1.12) apart from the ellipticity) we had not specified this in such remark. We have amended this modifying the whole Remark~3.4.


\vspace{2cm}


During the last revision, we realized that some comments in Remark~3.4 could be somewhat misleading and we decided to rewrite it in a more clear manner. The issue concerns estimates (3.8) and (3.9) in the old version of the document. Such estimates require some regularity on the kernel of the operator $L_K$ in order to hold. Although this regularity is fulfilled by the operators that we consider in this paper (that is, satisfying the convexity assumption (1.12) apart from the ellipticity), we had not specified this in such remark. We have amended this modifying the whole Remark~3.4, specifying the regularity of the kernel $K$. In addition, to simplify, we have removed estimate (3.8), which was not needed (the previous estimate (3.6) suffices for our purposes).



We realize that the regularity of the kernel was not specified in Theorems 1.3 and 1.4 and we only assume the positivity condition (1.13). Instead of adding the regularity condition we have preferred to change tha hypothesis replacing the positivity condition (1.13) by the convexity condition (1.12). In order to clarify it, we have added a footnote where we explain that the results also hold when instead of the convexity condition we assume the positivity condition plus some regularity on the kernel. Note that as it is explained in the paper, we believe that in fact conditions (1.12) and (1.13) are equivalent, although we are only able to prove it when the kernel is a $C^2$ function (see Theorem 1.1).  
\end{document}          

